sensiAnPaper1All

### 2016-03-08 paper1_results_figs.Rmd
figures

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #try facetted showing generation differences, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #?viridis
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             geom_point(alpha=1)  
           )

>>>>

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$abs_diff==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.25 <- 1
  df_same$seq_better_mixA0.25 <- 1
  #rbind them back onto other dataset
  ggSubset <- rbind( ggSubset, df_same)

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

    #NOW what if I subset the 0 values & fit a linear model to it
    #could that be used to decide between the 2 strategies ?
    #I might even be able to do the lm plot within ggplot

    #trickiness I have is that I have previously put 0 values in the adptive mix better plot 
    #which is maybe a little misleading anyway
    #and also means that I only get the lm line in the one plot
    #maybe what I can do is add the zeros into both plots then  will get lines in both
    #might even be good to overplot the zero values after
    #or even remove the zero values ?

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

# doing the lm outside of ggplot    
df_same = ggSubset[which(ggSubset$abs_diff==0),]
x1=df_same$exposure 
y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

l_mod <- lm(y1 ~ x1)
l_mod$coefficients
#(Intercept)           x 
#  0.9790948   0.6095132

x2 <- seq(0,1,0.1)
#approximation
y2 <- 0.6*x2+0.98
plot(x2,y2)

### 2016-03-08 paper1_results_figs_slimmed.Rmd
figures

## Main Figures for paper 1 : version 2 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.

@@

\pagebreak
## Fig. x1 Time-to-resistance across all input values

@@

\pagebreak
## Fig x2 PRCC analysis for time-to-resistance 0.25 for sequential and mixture strategies

@@

\pagebreak
## Fig. x3 How time-to-resistance is effected by input values for each insecticide use strategy

@@

\pagebreak
## Fig. x4 PRCC difference in time-to-resistance 0.25 between sequential and adaptive mixture strategies

@@

\pagebreak
## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises faster under adaptive mixture or sequential strategies

```{r, eval=TRUE, echo=FALSE, fig.height=5}

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #try facetted showing generation differences, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix\nslower to reach resistance',
                                                                        '1'='sequential\nslower to reach resistance'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #?viridis
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in\ngenerations\nto reach\nresistance\nthreshold")) + 
             theme_bw() +
             #theme_minimal() +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') +             
             geom_point(alpha=1, size=0.5)  
           )

>>>>

## Main Figures for paper 1 : version 3 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture, switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and dominance have the greatest on time-to-resistance as shown in PRCC analyses.
1. Effectiveness of the insecticides is the one input that can change the average relative positioning of the strategies a) sequential and b) adaptive mixture. Below an effectiveness of ~0.55 to 0.6 sequential takes longer to reach the resistance threshold, and above this the adaptive mixture takes longer. 
1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.

@@

\pagebreak

## Fig. x1 Time-to-resistance across all input values

@@

\pagebreak

## Fig x2 PRCC analysis for time-to-resistance 0.25 for sequential and mixture strategies

@@

\pagebreak

## Fig. x3 How time-to-resistance is effected by input values for each insecticide use strategy

@@

\pagebreak

## Fig. x4 PRCC difference in time-to-resistance 0.25 between sequential and adaptive mixture strategies

@@

\pagebreak

## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises slower under adaptive mixture or sequential strategies

1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.

```{r, eval=TRUE, echo=FALSE, fig.height=6}

@@

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$abs_diff==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.25 <- 1
  df_same$seq_better_mixA0.25 <- 1
  #rbind them back onto other dataset
  ggSubset <- rbind( ggSubset, df_same)

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_diff))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance slower','1'='sequential\nresistance slower'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='lightgrey', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```
Grey triangles are those runs in which resistance reached the threshold at the same time in the two strategies (and are repeated in both panels). The grey line is a linear model through these same points.

## Fig. x6 Classification Tree
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5}

  #code copied from sensiAnPaper1All

  require('plyr')

  ## is mix adaptive better than sequential ?
  #T/F
  resistBetterMix_ASeqBoolean <- resistPointsMix_A > resistPointsSeq
  #convert to 0/1
  resistBetterMix_ASeq <- plyr::aaply(resistBetterMix_ASeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq) <- gsub('gen','betterMix_ASeq', rownames(resistBetterMix_ASeq))

  #replace 0s & 1s with mixture/sequence to make tree plot clearer
  repMix <- function(x){
    x[x==0] <- 'sequence'
    x[x==1] <- 'mixture'
    x
  }

  resistBetterMix_ASeq <- repMix(resistBetterMix_ASeq)

  treeInput <- rbind( treeInput, resistBetterMix_ASeq )

  #transpose
  treeInput <- t(treeInput)

  #convert to a dataframe
  treeInput <- data.frame(treeInput, stringsAsFactors = FALSE)

  require(rpart.plot)

  #convert predictor columns back to numeric
  #following this above : replace 0s & 1s with mixture/sequence to make plot clearer
  results_columns <- substr(names(treeInput),1,6) %in% 'better'
  input_columns <- !results_columns
  treeInput[,input_columns] <- lapply(treeInput[,input_columns],as.numeric) 
  treeInput[,results_columns] <- lapply(treeInput[,results_columns],as.factor)

  #create string with predictor names in
  treePredictorString <- paste(colnames(treeInput)[input_columns], collapse="+")

  #just doing for one strategy, sensiAnPpaer1All.Rmd does for a bunch
  treeResponse <- rownames(resistBetterMix_ASeq)[2] #2 is 25%

  tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
  #treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])

  #http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree
  #A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.

  cpOptimal <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"CP"][1]

  treePruned <- prune(tree, cp=cpOptimal)

  #to set box colours
  cols <- ifelse(treePruned$frame$yval == 1, "red", "green3")

  #adds in no. scenarios correctly and incorrectly classified
  #prp(tree, extra=1, varlen = 10, main=treeResponse)
  #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
  #prp(treePruned, extra=1, varlen = 0, main=treeResponse, col=cols, border.col=cols)
  prp(treePruned, extra=1, varlen = 0, main='', box.col=cols, under=TRUE)

### 2016-03-08 resistanceModelNotesAndy.Rmd
figures

### TO DO  
~ check stackoverflow for getting mean into hexbin plot

~ communicate my concern to Ian that figures I've spent quite a long time on just go into supplementary material where few will see them. Can we think of a way of getting these into a paper themselves ? e.g. if this first paper is targeted at policy people can we get a 2nd paper that is targetted at biologists and explores mechanisms ?

~ can I change order of strategies in legend ?
~ can I facet the smoothed scatter plots to get them to take up less space and avoid repeating legend ?
~~ or I may be able to use a similar plot_grid() method

>>>>

~ changed order of strategies in legend

~ created new killer figure with added effectivenesses on the y & exposure on x.

** 8/3/2016 **

~ add Curtis fig2 params to killer figure
~ tricky adding to legend or labelling
~ can I get legend for killer figure beneath ?
~ can I derive a line for the border between when seq & mix better by fitting a line to the 0 values ?
~ get the classification tree that matches my killer figure

### TO DO

~ improve classification tree heading
~ add classification tree for >20% better

~ check with Ian what the best resistance threshold to focus on is. In Curtis Fig2 it is 50%. I have been using the 25% in my figs (but I could change). WHO thresholds are :

~ I just had a thought. Is the effectiveness effect additive ? i.e. do 2 insecticides of effectiveness 0.7 have the same effect e.g. as one of 1 and the other of 1.4 ?

~ maybe communicate my concern to Ian that figures I've spent quite a long time on just go into supplementary material where few will see them. Can we think of a way of getting these into a paper themselves ? e.g. if this first paper is targeted at policy people can we get a 2nd paper that is targetted at biologists and explores mechanisms ?

~ can I facet the smoothed scatter plots to get them to take up less space and avoid repeating legend ?
~~ or I may be able to use a similar plot_grid() method

### 2016-03-08 sensiAnPaper1All.Rmd
figures

  rowSums(resistBetterMix_1Seq)/ncol(resistBetterMix_1Seq)
  #100runs
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #               .178                  .232                  .238 
  #new100
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #              0.18                 0.24                 0.25 
  #new1000
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #             0.223                0.245                0.243

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix_ASeqBoolean <- resistPointsMix_A > resistPointsSeq
  #convert to 0/1
  resistBetterMix_ASeq <- plyr::aaply(resistBetterMix_ASeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq) <- gsub('gen','betterMix_ASeq', rownames(resistBetterMix_ASeq))

  rowSums(resistBetterMix_ASeq)/ncol(resistBetterMix_ASeq)  
  #1000runs
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #             0.471                0.568                0.551 
  #new100
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #              0.58                 0.57                 0.52 
  #new1000
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #             0.558                0.563                0.534

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix_2SeqBoolean <- resistPointsMix_2 > resistPointsSeq
  #convert to 0/1
  resistBetterMix_2Seq <- plyr::aaply(resistBetterMix_2SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_2Seq) <- gsub('gen','betterMix_2Seq', rownames(resistBetterMix_2Seq))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix_2Seq)/ncol(resistBetterMix_2Seq)
  #100runs
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #                .794                  .726                  .673  
  #new100
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #              0.83                 0.79                 0.72 
  #new1000
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #             0.820                0.747                0.677

@@

  #check2
#   #what is the absolute difference between mix3 & sequential ?
#   resistDifferenceMix_2Seq <- resistPointsMix_2 - resistPointsSeq
#   
#   #check3 is their a difference between the mix & the individual strategies
#   #looks mostly plausible, occasionally there are 0s
#   resistDifferenceMix_1I1 <- resistPointsMix_1 - resistPointsI1
#   resistDifferenceMix_1I2 <- resistPointsMix_1 - resistPointsI2

  ## is mix2 better than sequential ?  
  # I might expect it to be similar to mix3

@@

  #replace 0s & 1s with mixture/sequence to make plot clearer
  repMix <- function(x){
    x[x==0] <- 'sequence'
    x[x==1] <- 'mixture'
    x
  }

>>>>

  rowSums(resistBetterMix_1Seq)/ncol(resistBetterMix_1Seq)

  #new1000
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #             0.223                0.245                0.243

  ## is mix adaptive better than sequential ?
  #T/F
  resistBetterMix_ASeqBoolean <- resistPointsMix_A > resistPointsSeq
  #convert to 0/1
  resistBetterMix_ASeq <- plyr::aaply(resistBetterMix_ASeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq) <- gsub('gen','betterMix_ASeq', rownames(resistBetterMix_ASeq))

  rowSums(resistBetterMix_ASeq)/ncol(resistBetterMix_ASeq)  
  #new1000
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #             0.558                0.563                0.534

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix_2SeqBoolean <- resistPointsMix_2 > resistPointsSeq
  #convert to 0/1
  resistBetterMix_2Seq <- plyr::aaply(resistBetterMix_2SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_2Seq) <- gsub('gen','betterMix_2Seq', rownames(resistBetterMix_2Seq))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix_2Seq)/ncol(resistBetterMix_2Seq)
  #new1000
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #             0.820                0.747                0.677

@@

  #check2
#   #what is the absolute difference between mix2 & sequential ?
#   resistDifferenceMix_2Seq <- resistPointsMix_2 - resistPointsSeq
#   
#   #check3 is their a difference between the mix & the individual strategies
#   #looks mostly plausible, occasionally there are 0s
#   resistDifferenceMix_1I1 <- resistPointsMix_1 - resistPointsI1
#   resistDifferenceMix_1I2 <- resistPointsMix_1 - resistPointsI2

@@

  #replace 0s & 1s with mixture/sequence to make tree plot clearer
  repMix <- function(x){
    x[x==0] <- 'sequence'
    x[x==1] <- 'mixture'
    x
  }
